\documentclass[a4paper,skipsamekey,11pt,english]{curve}

\usepackage[empty]{fullpage}

\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{fontawesome5}

\usepackage{multicol}
\usepackage{bookmark}

% fonts
\usepackage[T1]{fontenc}
\usepackage[p,osf,swashQ]{cochineal}
\usepackage{cabin}
\usepackage[varqu,varl,scale=0.9]{zi4}

% maybe use this?
\usepackage[most]{tcolorbox}

% colors
\usepackage[table]{xcolor}
\definecolor{base1}{HTML}{93a1a1}
\definecolor{base03}{HTML}{002b36}
\definecolor{green}{HTML}{859900}
\definecolor{blue}{HTML}{268bd2}
\definecolor{orange}{HTML}{cb4b16}
\definecolor{red}{HTML}{dc322f}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}

\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.4in}

\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\tabcolsep}{0pt}
\setlength{\footskip}{3.7pt}
\raggedbottom
\raggedright

\input{glyphtounicode}
\pdfgentounicode=1

\hypersetup{
  colorlinks=false,
  pdfborder={0 0 0},
}

\newcommand{\allTheInfo}[3]{
  \begin{center}
    {\Huge\color{red} #1} \hfill {
      \begin{minipage}{3in}
        #2
      \end{minipage}
    }
    \vspace{10pt}
    \begin{tcolorbox}[
      sharp corners,
      boxrule=0mm,
      enhanced,
      borderline north={1pt}{0pt}{blue},
      borderline south={1pt}{0pt}{blue},
      borderline west={0pt}{0pt}{base1!10},
      borderline east={0pt}{0pt}{base1!10},
    ]
      \begin{center}
        \vspace{-5pt}
        \Large{#3}
        \vspace{-5pt}
      \end{center}
    \end{tcolorbox}
  \end{center}
}

\newcommand{\makeSkillRow}[3]{
  {$\Rightarrow$#1} & {$\Rightarrow$#2} & {$\Rightarrow$#3}\\
}

\newcommand{\makeWorkHistoryTitle}[5]{
  \begin{tcolorbox}[colback=base1!10,colframe=base1!10,frame hidden]
    {\color{blue}\textbf{#1}}, \textbf{#2} - #3 \hfill #4\\
    {\small\textit{#5}}
  \end{tcolorbox}
}

\newcommand{\makeFooter}[4]{
  \fancyfoot[R]{
    \color{base1}{
      #1 ~ | ~ #2 ~ | ~ #3 ~ | ~ #4 ~ | ~ $\thepage$ of $2$
    }
  }
}


\titleformat
{\section} % command
[display] % shape
{\bfseries\Large\itshape} % format
{} % label
{0em} % sep
{
  \vspace{-5pt}
  \color{green}
  \raggedright\Large\bfseries
} % before-code
[
  \vspace{-10pt}
  {
    % Stollen from the example resume by LianTze Lim (liantze@gmail.com)...
    % WAY cooler than a simple \hline.
    \begin{tikzpicture}[baseline]
      \shade[left color=blue!60!white, right color=white] rectangle (17,2.5pt);
    \end{tikzpicture}
  }
] % after-code

% I'm not a wizard, so I can't call this a
% Curriculum Vitae
\title{Resume}

\begin{document}

  \allTheInfo{
    Daniel Robertson
  }{
    \href{tel:5714519241}{
      \raisebox{-0.05\height} \faPhone\ 571-451-9241} ~ | ~
    \href{mailto:dan@dlrobertson.com}{
      \raisebox{-0.15\height} \faEnvelope\ dan@dlrobertson.com}\\
    \href{www.linkedin.com/in/daniellutherrobertson/ }{
      \raisebox{-0.15\height} \faLinkedin\ @daniellutherrobertson }\\
    \href{https://github.com/dlrobertson}{
      \raisebox{-0.15\height} \faGithub\ @dlrobertson} ~ | ~
    \href{https://dlrobertson.com}{
      \raisebox{-0.15\height} \faGlobe\ https://dlrobertson.com}
  }{
    \color{base03}\textbf{Open-Source Kernel Developer}
  }

  \textbf{Perseverant and purposeful software engineer} with expertise in Linux kernel
  development, open-source collaboration, software performance and scalability,
  cross-team collaboration, and debugging and troubleshooting. Confidently
  tackle detail-oriented challenges, demystifying and integrating complex
  issues into broader projects and facilitating team member contribution and
  collaboration. Customer-focused engineer who stays close to the problem and
  generates solutions that exceed client expectations.
  \begin{center}
    \setlength{\tabcolsep}{1em}
    \begin{tabular}{ l l l }
      \makeSkillRow{
        Linux Kernel Development
      }{
        C Programming
      }{
        Technical Writing
      }
      \makeSkillRow{
        Open Source Collaboration
      }{
        Rust Programming
      }{
        Community Engagement
      }
      \makeSkillRow{
        File System Development
      }{
        Network Protocols (IPv6)
      }{
        Cross-Functional Collaboration
      }
      \makeSkillRow{
        Debugging \& Troubleshooting
      }{
        Fuzz Testing
      }{
        Hypervisor Development
      }\\
    \end{tabular}
  \end{center}

  \section{Open Source Highlights}
  \begin{center}
    {\rowcolors{2}{white}{base1!10}
    \setlength{\tabcolsep}{1em}
    \begin{tabular}{c!{\color{blue}\vrule}c}
      \arrayrulecolor{blue}
      \vspace{1pt}
      {
       \begin{tabular}{c}
         \color{base03}\textbf{Linux Kernel}
       \end{tabular}
      } & {
        \begin{minipage}{5in}
          \vspace{5pt}
          \begin{itemize}
            \item \textbf{Authored and upstreamed the BMA400 Accelerometer IIO
            driver} to the Linux kernel, enabling users to use the device with
            either I2C or SPI serial communiation protocols.
            \item \textbf{Improved system stability and robustness} of
            \texttt{bcachefs} by identifying and resolving several kernel
            bugs found during fuzz testing.
          \end{itemize}
        \end{minipage}
      }
      \\
      \hline
      {
       \begin{tabular}{c}
         \color{base03}\textbf{Rust Compiler}
       \end{tabular}
      } & {
        \begin{minipage}{5in}
          \vspace{5pt}
          \begin{itemize}
            \item \textbf{Closed critical gap in interoperability with C} by
            implementing C \texttt{va\_list} and variadic functions, enhancing
            ability to export C APIs.
            \item \textbf{Optimized stability and functionality of Rust language}
            by rectifying several internal compiler errors.
          \end{itemize}
        \end{minipage}
        \vspace{1pt}
      }
      \\
      \hline
      {
       \begin{tabular}{c}
         \color{base03}\textbf{Smoltcp}
       \end{tabular}
      } & {
        \begin{minipage}{5in}
          \vspace{5pt}
          \begin{itemize}
            \item \textbf{Implemented IPv6 support}, refining Redox OS’
            networking capabilities.
            \item \textbf{Assisted with project maintenance} and coordinated
            contributors, fostering collaboration in open-source environment.
          \end{itemize}
        \end{minipage}
        \vspace{1pt}
      }
      \\
      \hline
      {
       \begin{tabular}{c}
         \color{base03}\textbf{Mythril}
       \end{tabular}
      } & {
        \begin{minipage}{5in}
          \vspace{5pt}
          \begin{itemize}
            \item \textbf{Designed host guest ACPI table parsing and building},
            enabling virtual machines to accurately detect and allocate system
            resources.
            \item \textbf{Directed initial development efforts} and delegated
            smaller tasks, cultivating teamwork among volunteers.
          \end{itemize}
        \end{minipage}
        \vspace{1pt}
      }
      \\
    \end{tabular}}
  \end{center}

  \section{Work Experience}
  \makeWorkHistoryTitle
    {Senior Software Engineer}
    {MOZILLA}
    {San Francisco, CA (Remote)}
    {Apr. 2022–Present}
    {
      Non-profit software community promoting exclusively free software and open
      standards with 40K global active contributors. Best known for Firefox web
      browser, Thunderbird email client, Bugzilla bug tracking system, Gecko
      layout engine, and Pocket “read-it-later-online” service.
    }
  \textbf{Hired} to maintain the asynchronous panning and zooming (scrolling)
  component of Firefox web browser after volunteering on several Mozilla
  open-source projects, including Servo and the Rust Compiler.

  \begin{itemize}
    \item \textbf{Provided reliable product up-time} by resolving incoming bugs
    and collaborating remotely with 3 software engineer team members to triage,
    troubleshoot, and debug issues.
    \item \textbf{Upheld user functionality} by aligning patches with web
    specifications and writing C++ code to fine-tune performance and address
    problems.
    \item \textbf{Improved web compatibility} across multiple browsers by
    contributing to web speifications and test frameworks, with a focus on
    the handling of \texttt{Blob}'s in the \texttt{fetch} specification.
  \end{itemize}

  \makeWorkHistoryTitle
    {Member of the Technical Staff}
    {STAR LAB, A WIND RIVER COMPANY}
    {Washington, DC}
    {Apr. 2019–Apr. 2022}
    {
      Provider of cybersecurity solutions for protecting Linux-based systems
      in mission-critical environments.
    }
  \textbf{Hired} to maintain custom Linux kernel-based security module and
  implement 2 file overlay filesystems an authenticated filesystem and an
  encrypted file system. Allied with 3–4 technical staff members in managing
  high-security contracts.

  \begin{itemize}
    \item \textbf{Boosted performance and scalability} of complex
    implementations overfile systems, guiding customers through the
    integration process and debugging live systems.
    \item \textbf{Improved Linux security module performance} by developing
    kernel framework to evolve from experimental phase to tangible,
    sellable product.
  \end{itemize}

  \makeWorkHistoryTitle
    {Machine Intelligence Engineer}
    {EMBEDDED INTELLIGENCE}
    {Washington, DC}
    {May 2018–Apr. 2019}
    {
      Cutting-edge R\&D company enhancing safety and security of
      A\-enabled systems.
    }
  \textbf{Joined} industry contact and friend in supporting DARPA research
  projects by formulating secure data pipelines and web crawlers to gather
  large-scale current and historical data from public archives.

  \begin{itemize}
    \item \textbf{Informed strategic decision\-making in research initiatives}
    by enhancing accuracy algorithms and designing pipelines that processed
    large\-scale datasets in partnership with machine learning experts.
    \item \textbf{Strengthened research proposals} that involved applying
    machine learning techniques to data collected from network traffic
    with in\-depth knowledge of network protocols.
  \end{itemize}

  \makeWorkHistoryTitle
    {Software Engineer}
    {TRIPWIRE}
    {Atlanta, GA}
    {May 2016–Jun. 2018}
    {
      Provider of cybersecurity risk management, helping organizations build
      security, compliance, and operational efficiency.
    }

  \textbf{Recruited} as network security product subject matter expert, using
  protocols to gather device information and evaluate risk of malicious intent
  and use. Collaborated with 20 software engineers and managers to remotely
  serve clients.

  \begin{itemize}
    \item \textbf{Upheld system reliability and minimized downtime for customers}
    by resolving complex memory issues in network devices using remote debugging
    techniques and code analysis to identify and fix problems.
    \item \textbf{Maintained high system performance and customer satisfaction} by
    providing on-call engineering support to troubleshoot and resolve urgent
    customer concerns.
  \end{itemize}

  \makeWorkHistoryTitle
    {ORISE Fellow}
    {CENTERS FOR DISEASE CONTROL \& PREVENTION (CDC)}
    {Atlanta, GA}
    {Sept. 2014–May 2016}
    {
      Provider of cybersecurity risk management, helping organizations build
      security, compliance, and operational efficiency.
    }
  \textbf{Hired} as a new graduate to pair with staff and receive hands\-on
  research experience.

  \begin{itemize}
    \item \textbf{Cut data entry time by 50\%} by writing programs to
    automatically input survey data into forms, eliminating need for
    double student entry.
  \end{itemize}

  \section{Education}
  \begin{tcolorbox}[colback=base1!10,colframe=base1!10,frame hidden]
    {\color{base03}\textbf{GEORGE MASON UNIVERSITY}} ~ – ~ Fairfax, VA\\
    \small Master of Public Health in Epidemiology ~ | ~
    Graduate Certificate in Biostatistics ~ | ~
    Bachelor of Science in Community Health
  \end{tcolorbox}

  \makeFooter{Daniel Robertson}{Waynesboro, VA}{571-451-9241}{dan@dlrobertson.com}
\end{document}
